---
title: "Eating Out"
author: "Dorothy Decker"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```


```{r, eval=TRUE}
#GSS <-(read_dta(file="GSS1998.dta"))
GSS<- readstata13::read.dta13(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

##Graphical 

### Plot barplots

#### Plot barplots tigerstats way

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```


In this set of graphical data, we can interpret that there is a higher frequency of white people eating out in comparison to the black demographic, as well as other. The Blue bar is white people in this graph, which shows how many say yes to eating out. In the second plot, we can see that there is still a higher percentage of white people saying yes in comparison to the other races. 

#### Plot barplots ggplot way

```{r}
dd2 <- mydata %>% group_by(race,eatout) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=race,y=eatout,fill=eatout))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=race,y=prcnt*100,fill=eatout)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  
Looking at this second set of graphical data, it continues to show that white people are more prone to saying yes to outing out, while other races and black people are saying no. There are still black people saying yes, there is just less black people saying yes in comparison to white.

### Numerical Summaries  

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```


Now with this numerical data, we are still seeing more white people say yes in comparison to the other races. For example, there are 81.75% white people saying yes, while there are 11.76% black people saying yes, and in the other category 6.49%. 

## Inferential  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We have a low P value of 2.287e-06. The Chi-squared test shows the # of people that said no and yes and which race they are.  

```{r}
fisherXY(mydata$race,mydata$eatout)
```



The P value of white is greater than 0.05. The P value is lower for black. The white and black have a difference of 2.2 eating out. The odds between Black and White is somewhere between .4 and 1.49, these two methods ar very similar to eachother. 



## Conclusion

Today in class we had to import our own data and use that data to answer questions on it. We used our template Cat_Cat in order to get different types of data to be able to observe the data we imported. With this said, we were able to statistically find a difference between the races based on our different sets of results.
